\vspace{-2cm} Government websites as data: A methodological pipeline for collection, processing, and text analysis

### 2017-12-27 paper/tables/stmTopWordsINRep.tex
results for IN (with population in the stm)

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 15:36:58 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
0.024 & 0.019 & 0.019 & 0.016 & 0.016 & 0.016 & 0.015 & 0.014 \\ 
  \hline
motion & plan & inc & request & council & traffic & build & inform \\ 
  second & zone & electr & board & citi & amp & histor & pleas \\ 
  made & applic & build & member & ordin & vehicl & preserv & will \\ 
  approv & properti & construct & servic & common & stop & wall & contact \\ 
  mayor & approv & home & street & councilor & sign & materi & use \\ 
  present & sign & street & approv & amend & road & paint & can \\ 
  state & site & meridian & purchas & resolut & block & roof & email \\ 
  will & locat & servic & citi & adopt & signal & structur & site \\ 
  citi & commiss & west & move & wherea & street & locat & phone \\ 
  council & file & main & good & approv & driver & window & card \\ 
   \hline
\end{tabular}
\caption{Top Republican topics and words (Indiana), according to STM. 
The words are the top words for the most Democratic/Republican topic, determined
by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINRep}
\end{table}

>>>>

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Tue Dec 26 20:59:22 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
0.023 & 0.021 & 0.019 & 0.017 & 0.017 & 0.014 & 0.013 & 0.012 \\ 
  \hline
library & foot & team & ave & request & board & amp & building \\ 
  stream & sign & game & inc & board & meeting & traffic & historic \\ 
  obj & use & play & cross & member & member & stop & build \\ 
  length & lot & league & creek & service & committee & vehicle & material \\ 
  branch & building & camp & construction & street & council & block & preservation \\ 
  type & zone & class & blvd & approve & commission & sign & wall \\ 
  flag & area & age & park & city & meet & airport & roof \\ 
  filter & district & must & lake & purchase & public & ave & window \\ 
  rim & parking & child & hill & move & director & theft & floor \\ 
  page & residential & participant & ridge & good & president & signal & new \\ 
   \hline
\end{tabular}
\caption{Top Republican topics and words (Indiana), according to STM. 
The words are the top words for the most Democratic/Republican topic, determined
by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINRep}
\end{table}
